### 2020-02-25 thesis/content/chapter-related-work.tex
minor additions

If we increase the \acs{wl}-dimension to $k = 2$, the described 1-\acs{wl} restrictions no longer apply.
2-\acs{wl} is able to distinguish more than $1 - \mathcal{O}(\nicefrac{1}{n})$ of the regular $n$-vertex graphs~\cite[cor.~1.8.6]{Immerman1990} and can even count cycles.
\begin{prop}[see \citet{Fuerer2017}]\label{prop:related:wl2-cycle-count}
	2-\acs{wl} is able to count $m$-cycles for $m \leq 6$ but it cannot detect 8-cycles.
	There are no results regarding 7-cycles.
\end{prop}
\begin{hproof}
	We refer to \citet{Fuerer2017} for the full proof.
	Only the idea behind triangle and 4-cycle counting is outlined here to give an intuition for why \cref{prop:related:wl2-cycle-count} holds.
	Note that the 2-\acs{wl} neighbors of each edge $(v, w) \in \mathcal{E}_G$ correspond to all possible paths $(v, u, w)$ of length 2, i.e.\ all possible triangles.
	By \cref{defn:related:wlk-refine} there must thus be a color subset $C^{\triangle}_j \subseteq \mathcal{C}$ representing that an edge is involved in exactly $j$ triangles after one refinement step.
	2-\acs{wl} then trivially counts triangles by setting $g(\mathit{dist}_\chi) = \frac{1}{3} \sum_j j \sum_{c \in C^{\triangle}_j} \mathit{dist}_\chi(c)$ to satisfy \cref{defn:related:wl-compute}.
	Analogously for 4-cycles, let $C^{\square}_j \subseteq \mathcal{C}$ be the colors indicating a non-edge $(v, w) \notin \mathcal{E}_G$ with $j$ common vertex neighbors $u \in \Gamma_G(v) \cap \Gamma_G(w)$.
	The number of 4-cycles is then determined by the colors of the diagonals through them via $g(\mathit{dist}_\chi) = \frac{1}{2} \sum_{j \geq 2} \binom{j}{2} \sum_{c \in C^{\square}_j} \mathit{dist}_\chi(c)$.
	Using a similar but more involved combinatorial argument requiring multiple color refinement steps, 5- and 6-cycle counting can be shown.
\end{hproof}
As we just saw, 2-\acs{wl} is significantly more powerful than 1-\acs{wl}.
By \cref{prop:related:wl-upper} there are of course still 2-\acs{wl} indistinguishable graphs;
among others those are the strongly regular graphs $\mathit{srg}_{n, d, \lambda, \mu}(G)$.
\begin{defn}
	$\begin{aligned}[t]
		\mathit{srg}_{n, d, \lambda, \mu}(G) \iff\ & {|\mathcal{V}_G|} = n \quad\land\quad \forall v \in \mathcal{V}_G: {|\Gamma_G(v)|} = d \\
		&\land \forall (v, w) \in \mathcal{E}_G: {|\Gamma_G(v) \cap \Gamma_G(w)|} = \lambda \\
		&\land \forall (v, w) \in \mathcal{V}_G^2 \setminus \mathcal{E}_G: {|\Gamma_G(v) \cap \Gamma_G(w)|} = \mu
	\end{aligned}$
\end{defn}
Generally this restriction of 2-\acs{wl} is not an issue since strongly regular graphs do not appear in typical \ac{gcr} datasets.
Lastly there are few results regarding the classes of distinguishable graphs and computable functions for higher \ac{wl}-dimensions.
For $k = 3$, \citet{Kiefer2017} have shown that all planar graphs can be distinguished.

@@

>>>>

If we increase the \acs{wl}-dimension to $k = 2$, the described 1-\acs{wl} restrictions no longer apply.
2-\acs{wl} is able to distinguish more than $1 - \mathcal{O}(\nicefrac{1}{n})$ of the regular $n$-vertex graphs~\cite[cor.~1.8.6]{Immerman1990} and can even count cycles.
\begin{prop}[see \citet{Fuerer2017} and \citet{Arvind2019}]\label{prop:related:wl2-cycle-count}
	2-\acs{wl} is able to count $m$-cycles for $m \leq 7$ but it cannot detect 8-cycles.
\end{prop}
\begin{hproof}
	Only the idea behind triangle and 4-cycle counting is outlined here to give an intuition for why \cref{prop:related:wl2-cycle-count} holds.
	Note that the 2-\acs{wl} neighbors of each edge $(v, w) \in \mathcal{E}_G$ correspond to all possible paths $(v, u, w)$ of length 2, i.e.\ all possible triangles.
	By \cref{defn:related:wlk-refine} there must thus be a color subset $C^{\triangle}_j \subseteq \mathcal{C}$ representing that an edge is involved in exactly $j$ triangles after one refinement step.
	2-\acs{wl} then trivially counts triangles by setting $g(\mathit{dist}_\chi) = \frac{1}{3} \sum_j j \sum_{c \in C^{\triangle}_j} \mathit{dist}_\chi(c)$ to satisfy \cref{defn:related:wl-compute}.
	Analogously for 4-cycles, let $C^{\square}_j \subseteq \mathcal{C}$ be the colors indicating a non-edge $(v, w) \notin \mathcal{E}_G$ with $j$ common vertex neighbors $u \in \Gamma_G(v) \cap \Gamma_G(w)$.
	The number of 4-cycles is then determined by the colors of the diagonals through them via $g(\mathit{dist}_\chi) = \frac{1}{2} \sum_{j \geq 2} \binom{j}{2} \sum_{c \in C^{\square}_j} \mathit{dist}_\chi(c)$.
	Using a similar but more involved combinatorial argument requiring multiple color refinement steps, 5-, 6- and 7-cycle counting can be shown.
\end{hproof}
As we just saw, 2-\acs{wl} is significantly more powerful than 1-\acs{wl}.
By \cref{prop:related:wl-upper} there are of course still 2-\acs{wl} indistinguishable graphs;
among others those are the strongly regular graphs $\mathit{srg}_{n, d, \lambda, \mu}(G)$.
\begin{defn}
	$\begin{aligned}[t]
		\mathit{srg}_{n, d, \lambda, \mu}(G) \iff\ & {|\mathcal{V}_G|} = n \quad\land\quad \forall v \in \mathcal{V}_G: {|\Gamma_G(v)|} = d \\
		&\land \forall (v, w) \in \mathcal{E}_G: {|\Gamma_G(v) \cap \Gamma_G(w)|} = \lambda \\
		&\land \forall (v, w) \in \mathcal{V}_G^2 \setminus \mathcal{E}_G: {|\Gamma_G(v) \cap \Gamma_G(w)|} = \mu
	\end{aligned}$
\end{defn}
Generally this restriction of 2-\acs{wl} is not an issue since strongly regular graphs do not appear in typical \ac{gcr} datasets.
Lastly there are few results regarding the classes of distinguishable graphs and computable functions for higher \ac{wl}-dimensions.
For $k = 3$, \citet{Kiefer2017} have shown that all planar graphs can be distinguished.

@@

An alternative perspective on graph characterization is provided by \textit{spectral graph theory}.
